---
title: "Analysis of activity monitoring data"
output: html_document
---
###1.Loading and pre-processing the dataset
The following code reads the given activity.csv file and pre-processes it to produce appropriate structure for analysis. The date portion of the data is converted into date format. 


```{r echo=TRUE,results='hide'}
unzip("activity.zip")
data <- read.csv("activity.csv")
data$date <- as.Date(data$date)
```
###2. What is mean total number of steps taken per day?
For this part of the assignment, you can ignore the missing values in the dataset.

1.Calculate the total number of steps taken per day. 
2.If you do not understand the difference between a histogram and a barplot, research the difference between them. Make a histogram of the total number of steps taken each day.
3.Calculate and report the mean and median of the total number of steps taken per day.

```{r, echo=TRUE}
ans <- sapply(split(data[1],data$date),sum,na.rm=TRUE)

hist(ans,main=paste("HISTOGRAM OF STEPS TAKEN"),xlab="STEPS",ylab="NUMBER OF DAYS")

mean(ans)
median(ans)
```

###3.What is the average daily activity pattern?
Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis).Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r, echo=TRUE}
mean_steps <- sapply(split(data$steps,data$interval),mean,na.rm=TRUE)
interval <- as.factor(data$interval)
mean_steps <- data.frame(mean_steps,interval)
plot(mean_steps$interval,mean_steps$mean_steps)
mean_steps[which.max(mean_steps$mean_steps),]

```
